\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-07 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

%%%
%%% FIGURE XXXXXX
%%%
\begin{figure}[ht]
\vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }
      \hbox{\hspace{1.0cm} (a) permeability map }}
\caption{3D channel flow \red{FIGS AND COMMENTS TO BE ADDED AS SOON AS THE SIMULATION FINISHES}. The domain contains 243056 \PN[1]{1} element-pairs.}
\label{fig:3DChannel_PermMesh}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
\begin{figure}[ht]
\vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/3D_channel_elem_planes_1.pdf} }
      \hbox{\hspace{5.0cm} }}
\caption{ XY and YZ planes in the middle of the domain at the end of simulation \red{t=$4.3$sec, but am I reading something wrong?} }
\label{fig:3DChannel_elem_planes}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%
%%% FIGURE XXXXXX
%%%
\begin{figure}[ht]
\vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }
      \hbox{\hspace{1.0cm} (a) permeability map }}
\caption{3D channel flow. The domain contains 243056 \PN[1]{1} element-pairs.}
\label{fig:3DChannel_PermMesh}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
%\begin{landscape}
\begin{figure}[ht]
\vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/3D_channel_elem_planes_1.pdf} }
      \hbox{\hspace{5.0cm} }}
\caption{ XY and YZ planes in the middle of the domain at the end of simulation \red{t=$4.3$sec, but am I reading something wrong?} }
\label{fig:3DChannel_elem_planes}
\end{figure}
%\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$$s and (b)t=$$s.}
\label{fig:3DChannel_darcy_vel}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{For the same time steps as in Figure \ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$$s and (b)t=$$s.}
\label{fig:3DChannel_sat}
\end{figure}
\end{landscape}
\clearpage
